\documentclass{article}

	\addtolength{\oddsidemargin}{-.875in}
	\addtolength{\evensidemargin}{-.875in}
		\addtolength{\textwidth}{1.75in}

	\addtolength{\topmargin}{-.875in}
	\addtolength{\textheight}{1.75in}
\title{\textbf {Deliverable 3}}



\begin{document}
\maketitle
\section*{\centering\textcolor{Code Review of F5 }}

\section{Overview}
The code review has been conducted of the Gamma Function program. Manual review has been done as well as automatic review has been done using CheckStyle Plugin. 
\section{Code Formatting}
There are the following points that has been observed while going through the code
\begin{itemize}
\item Use of alignment (left margin) has not been followed properly.
\item There are a lot of extra white spaces in the code.
\item Proper naming conventions (Pascal, CamelCase etc.) have been followed.
\item There are unnecessary comments in the code.
\item The readability of the code is very complex because the names of the function should be descriptive about the nature of the functionality being implemented in the method.
\item There are 1118 CheckStyle violation markers has been found in the code
\item The code is exceeding the limit of average LOC per class. We can see that the code is more than of 400 lines.
\end{itemize}


\section{Architecture}
It does not follow any separation of concerns principle. An architecture should have been implemented because of the maintainability purpose.
\section{Programming Code Style}
\begin{itemize}
\item The code was seen to have a lot of hard coded values. Enums or property files should have been used for hard coded values
\item It can be seen there are many if/else clauses for single line of statement. Ternary operators should have been used instead of that.
\item There are some meaningful documentation in source code.
\end{itemize}

\section{Non-Functional Requirements}
\begin{itemize}

 \item The same code has been repeated more than twice.
 \item Since the class file has more than 400 LOC henceforth it is tough to analyze and maintainability is affected.
 

\end{itemize}

\section{Quality attributes}
\begin{itemize}

\item The program implements unnecessary required functionality. Addition, Subtraction, Multiplication and Division implementations have been done that was not required which is adding the complexity of the code.
\item The program is functionally correct.
\item The program provides preventative error handling for user. It prompts message for complex operation.
\end{itemize}

% keywords can be removed
\section*{\centering\textcolor{Testing Review of F6 }}

\section{Testing Results}
\begin{itemize}

\item Junit5 framework has been used for testcases.
\item All the test cases have been passed.
\item The bulit-in function 'assertEquals' has been used to check all the responses.
\end{itemize}


\section{References}
\begin{itemize}
 \item Gee, T. (2019). Code review best practices | The ultimate software development tool. [online] Fogbugz.com. Available at: https://www.fogbugz.com/blog/code-review-best-practices/ [Accessed 2 Aug. 2019].

\item Evoke Technologies. (2019). Code Review Checklist – To Perform Effective Code Reviews. [online] Available at: https://www.evoketechnologies.com/blog/code-review-checklist-perform-effective-code-reviews/ [Accessed 2 Aug. 2019].

\item GitHub. (2019). saadkhan2005/SOEN6011Project. [online] Available at:$\\$ https://github.com/saadkhan2005/SOEN6011Project [Accessed 29 Jul. 2019].
\end{itemize}
\end{document}

